---
title: "Assignment3"
author: "Kirby Bartlett"
date: "May 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)

whale_data <- read_csv("HW3Data.csv")

```


binomial linear regression for part 1
```{r}
model_pt1 <- lm(vote ~ age + income + NEP + risk + bid, data = whale_data, family = "linear")

summary(model_pt1)

coeffs <- coefficients(model_pt1); coeffs

```

























Part 2:

```{r}

#assume vote = 1, all constants stay the same (cancel out) but risk reduction moved from 0% to 4%

bid_single = -(0.0007445*4)/-0.0010699

bid_single  
#2.78
#coeff11 is the risk, coeff 12 is the bid



```

Original Function
vote <- function(a,b,c,d,f,g,h,j,k,l,m){ 0.0099816(a) + -0.0201190(b) +-0.0162261(c) +0.0204401(d) +0.0088282(f) +0.0027386(g)+0.0074891(h)+ 0.0467922(j)+0.0158639(k)+ 0.0007445(l) +  -0.0010699(m) + 0.1196977
}

Bid equation
bid <- (vote – 0.0099816(agetofifty) - -0.0201190(agetoforty) - -0.0162261(agetosixty) -0.0204401(agetothrity) - 0.0088282(income_onepercent) -0.0027386(incomepoor) - 0.0074891(incomerich) - 0.0467922(income_veryrich) - 0.0158639(NEP) - 0.0007445(risk) - 0.1196977) / -0.0010699


Use 60% as your risk and know that that saves 15 whales. Solve. So 4% risk saves 1 whale

Part 3:
Pick three people and put in their info and solve for vote. Then set vote to 1 and solve for bid. 


```{r}
#row 17

bid1= (.5 + 0.0201190*1 - 0.0027386*1 - 0.0158639*30 - 0.0007445*20 - 0.1196977) /(-0.0010699)

bid1 #87.04

#row 230

bid2 = (.5- 0.0099816*1 - 0.0088282*1 - 0.0158639*23 - 0.0007445*60 - 0.1196977) / -0.0010699

bid2 #44.90

#row400

bid3 = (.5- 0.0158639*31 - 0.0007445*80 - 0.1196977) / -0.0010699

bid3 #159.86

```


Part 4:
Would you take the average of all parameters and solve for bid?
Tofifty and middle class would be the middle variables for categorical. Middle class is a reference level
```{r}
#find average NEP

avg_NEP <- mean(whale_data$NEP)
avg_NEP #38.366

#eguationb for average bid assuming average age is to fifty and income is middle class
bid_avg = (.70 - 0.0099816*1 - 0.0158639*38.366 - 0.0007445*60 - 0.1196977) / -0.0010699

bid_avg
#77.5621


```


Part 5:
Multiply average by 150,000
```{r}
total_wtp <- bid_avg *150000
total_wtp
#11,634,315

```

Part 6:
Compare answer in 5 to 7 million. The answer in part 5 is 11.6 million, so Santa Barbara residents are willing to pay 11.6 million to save whales, which outweighs the costs of $7 million to implement the VSR program. There is a net benefit of 4.6 million dollars to the community.


Part 7:
Is it $50 per ton? Because 50x20 tons carbon saved is 1,000 dollars which is the cost of going slower

Part 8:
60% risk reduction means 15 whales saved? Multiply what you found in part 2 by 15 to get the social benefit? Since there is no cost associated with the trade you can ignore the $7 million VSR cost.

```{r}
social_benefit <-bid_single*15
social_benefit
#41.75 which doesnt make sense

```

