---
title: "Assignment3"
author: "Kirby Bartlett"
date: "May 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)

whale_data <- read_csv("HW3Data.csv")

```


binomial linear regression for part 1
```{r}
model_pt1 <- lm(vote ~ age + income + NEP + risk + bid, data = whale_data, family = "linear")

summary(model_pt1)

```

























Part 2:

```{r}
coeffs <- coefficients(model_pt1); coeffs


vote <- function(a,b,c,d,f,g,h,j,k,l,m){ coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[12](m) + coeffs[1]
}


bid_fifteen<- function (a,b,c,d,e,g,h,j,k,l,m) {(1- (coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[11](m) + coeffs[1])/coeff[12])
}

bid_single<- bidfifteen/15


```

Original Function
vote <- function(a,b,c,d,f,g,h,j,k,l,m){ 0.0099816(a) + -0.0201190(b) +-0.0162261(c) +0.0204401(d) +0.0088282(f) +0.0027386(g)+0.0074891(h)+ 0.0467922(j)+0.0158639(k)+ 0.0007445(l) +  -0.0010699(m) + 0.1196977
}


Use 60% as your risk and know that that saves 15 whales. Solve. 
Have vote as 1 and solve for bid. Then divide by 15 to get value of 1 whale

Part 3:
Pick three people and put in their info and solve for vote. Then set vote to 1 and solve for bid. 
```{r}

vote1 <- function(a,b,c,d,f,g,h,j,k,l,m){ coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[12](m) + coeffs[1]
}


bid1 <- function (a,b,c,d,e,g,h,j,k,l,m) {(1- (coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[11](m) + coeffs[1])/coeff[12])
}

vote2 <- function(a,b,c,d,f,g,h,j,k,l,m){ coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[12](m) + coeffs[1]
}


bid2 <- function (a,b,c,d,e,g,h,j,k,l,m) {(1- (coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[11](m) + coeffs[1])/coeff[12])
}

vote3 <- function(a,b,c,d,f,g,h,j,k,l,m){ coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[12](m) + coeffs[1]
}


bid3 <- function (a,b,c,d,e,g,h,j,k,l,m) {(1- (coeffs[2](a) + coeffs[3](b) + coeffs[4](c) + coeffs[5](d) + coeffs[6](f) + coeffs[7](g) + coeffs[8](h) + coeffs[9](j) + coeffs[10](k) + coeffs[11](l) +  coeffs[11](m) + coeffs[1])/coeff[12])
}

bid1
bid2
bid3

```


Part 4:
Would you take the average of all parameters and plug that in to solve for vote, then set vote to 1 and solve for bid?

Part 5:
Multiply average by 150,000