---
title: "Assignment3"
author: "Kirby Bartlett"
date: "May 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)

whale_data <- read_csv("HW3Data.csv")

```


binomial linear regression for part 1
```{r}
model_pt1 <- lm(vote ~ age + income + NEP + risk + bid, data = whale_data, family = "linear")

summary(model_pt1)
```

<<<<<<< HEAD
```{r}
#pull coefficients out 
coeffs <- coefficients(model_pt1) ; coeffs

coeffs[5]
=======
coeffs <- coefficients(model_pt1); coeffs
>>>>>>> af9d3ad1145fa1dad5b619176d575639eac42e45


newdata <- data.frame(agetofifty=1,
                      agetoforty=0,
                      agetosixty=0,
                      agetothirty=0,
                      incomeone_percent=1,
                      incomepoor=0,
                      incomerich=0,
                      incomevery_rich=0,
                      NEP=40,
                      risk = 0.6,
                      bid=20)


predict(model_pt1, newdata)
```

<<<<<<< HEAD
=======
























>>>>>>> af9d3ad1145fa1dad5b619176d575639eac42e45
Part 2:

```{r}

#assume vote = 1, all constants stay the same (cancel out) but risk reduction moved from 0% to 4%

bid_single = -(0.0007445*4)/-0.0010699

bid_single  
#2.78
#coeff11 is the risk, coeff 12 is the bid



```

Original Function
vote <- function(a,b,c,d,f,g,h,j,k,l,m){ 0.0099816(a) + -0.0201190(b) +-0.0162261(c) +0.0204401(d) +0.0088282(f) +0.0027386(g)+0.0074891(h)+ 0.0467922(j)+0.0158639(k)+ 0.0007445(l) +  -0.0010699(m) + 0.1196977
}

Bid equation
bid <- (vote – 0.0099816(agetofifty) - -0.0201190(agetoforty) - -0.0162261(agetosixty) -0.0204401(agetothrity) - 0.0088282(income_onepercent) -0.0027386(incomepoor) - 0.0074891(incomerich) - 0.0467922(income_veryrich) - 0.0158639(NEP) - 0.0007445(risk) - 0.1196977) / -0.0010699


Use 60% as your risk and know that that saves 15 whales. Solve. So 4% risk saves 1 whale

Part 3:
Pick three people and put in their info and solve for vote. Then set vote to 1 and solve for bid. 


```{r}
#row 17

bid1= (.5 + 0.0201190*1 - 0.0027386*1 - 0.0158639*30 - 0.0007445*60 - 0.1196977) /(-0.0010699)

bid1 #114.87

#row 230

bid2 = (.5- 0.0099816*1 - 0.0088282*1 - 0.0158639*23 - 0.0007445*60 - 0.1196977) / -0.0010699

bid2 #44.90

#row400

bid3 = (.5- 0.0158639*31 - 0.0007445*60 - 0.1196977) / -0.0010699

bid3 #145.94

```

```{r}
#Table of the three bids
bid_df <- data.frame(round(bid1, 2), round(bid2, 2), round(bid3, 2))


```


Part 4:
Would you take the average of all parameters and solve for bid?
Tofifty and middle class would be the middle variables for categorical since they are median
use .5 is the average vote 
use mean NEP
```{r}
#find average NEP

avg_NEP <- mean(whale_data$NEP)
avg_NEP #38.366

#eguationb for average bid median age is tofifty median income is rich

bid_avg = (.5 - 0.0099816*1 -  0.0074891*1 - 0.0158639*38.366 - 0.0007445*60 - 0.1196977) / -0.0010699

bid_avg
#271.4953


```


Part 5:
Multiply average by 150,000
```{r}
total_wtp <- bid_avg *150000
total_wtp
#40724290

```

Part 6:
Compare answer in 5 to 7 million. The answer in part 5 is 39.7 million, so Santa Barbara residents are willing to pay 11.6 million to save whales, which outweighs the costs of $7 million to implement the VSR program. There is a net benefit of 32.7 million dollars to the community.


Part 7:
Is it $50 per ton? Because 50x20 tons carbon saved is 1,000 dollars which is the cost of going slower

Part 8:
Same number as #5
Value of offset carbon per ship is 1000 which is the same of the compliance cost per ship, $1000 so that cancels.

```{r}
total_wtp + 1000 - 1000

```

